\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-07 paper.qmd
Changed NLDR MNIST PaCMAP image

library(Rtsne)
library(uwot)
library(phateR)
library(patchwork)
library(langevitour)
library(colorspace)
library(kableExtra)
library(grid)
library(conflicted)
conflicts_prefer(dplyr::filter)
```

@@

position_df <- pacmap_minst_scaled |> 
  filter(ID %in% c(6475, 3311, 6489, 2347, 387, 
                          5239, 728, 517, 6369, 3055, 6345, 1761)) |>
  mutate(position = c(5, 9, 7, 8, 4, 11, 2, 6, 12, 10, 1, 3))

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1) #+ 
  # geom_text(data = position_df, 
  #           aes(x = PaCMAP1, y = PaCMAP2, label = position), 
  #           colour = "red", 
  #           size = 5)  
```

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "$2\\text{-}D$ layout from PaCMAP applied for the digit 1 of the MNIST dataset. Is this the best representation of the digit 1? The parameter setting is n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0."
#| label: fig-pacmap-author
#| fig-pos: H
#| out-height: 22%

>>>>

library(Rtsne)
library(uwot)
library(phateR)
library(patchwork)
library(png)
library(langevitour)
library(colorspace)
library(kableExtra)
library(grid)
library(conflicted)
conflicts_prefer(dplyr::filter)
```

@@

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1)

# read the png file from device 
left_top_img <- readPNG("figures/mnist/mnist_digit1_img_lt.png", native = TRUE)
center_img <- readPNG("figures/mnist/mnist_digit1_img_c.png", native = TRUE)
right_bottom_img <- readPNG("figures/mnist/mnist_digit1_img_rb.png", native = TRUE)

pacmap_plot_mnist <- pacmap_plot_mnist +
    inset_element(p = left_top_img, 
                  left = 0.8, 
                  bottom = 0.85, 
                  right = 0, 
                  top = 0.95) +
    inset_element(p = center_img, 
                  left = 1.2, 
                  bottom = 0.6, 
                  right = 0, 
                  top = 0.7) +
    inset_element(p = right_bottom_img, 
                  left = 1.7, 
                  bottom = 0.48, 
                  right = 0, 
                  top = 0.58)
```

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "$2\\text{-}D$ layout from PaCMAP applied for the digit 1 of the MNIST dataset with a specific parameter settings. The angle of the digit 1 varies along this structure. Images at the top-left of the $2\\text{-}D$ layout show the digit 1 angled more to the left, while images at the bottom-right show the digit 1 angled more to the right. Is this the best representation of the digit 1?"
#| label: fig-pacmap-author
#| fig-pos: H
#| out-height: 22%

### 2024-07-07 paper.tex
Changed NLDR MNIST PaCMAP image

\caption{\label{fig-pacmap-author}\(2\text{-}D\) layout from PaCMAP
applied for the digit 1 of the MNIST dataset. Is this the best
representation of the digit 1? The parameter setting is n\_components=2,
n\_neighbors=10, init=random, MN\_ratio=0.9, FP\_ratio=2.0.}

>>>>

\caption{\label{fig-pacmap-author}\(2\text{-}D\) layout from PaCMAP
applied for the digit 1 of the MNIST dataset with a specific parameter
settings. The angle of the digit 1 varies along this structure. Images
at the top-left of the \(2\text{-}D\) layout show the digit 1 angled
more to the left, while images at the bottom-right show the digit 1
angled more to the right. Is this the best representation of the digit
1?}
